Fossil-calibrated phylogeny and chromosome evolution of Onagraceae

### 2014-04-24 manuscript.tex
cleaning up some

%\journal{Journal of \LaTeX\ Templates}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

@@

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Phylogeny, divergence times, and chromosome evolution in Onagraceae}

@@

\address[berk]{1600 John F Kennedy Boulevard, Philadelphia}

@@

\paragraph{Supermatrix} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.

@@

@@

There are various bibliography styles available. You can select the style of your choice in the preamble of this document. These styles are Elsevier styles based on standard styles like Harvard and Vancouver. Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.

>>>>

\graphicspath{ {./figures/} }

\journal{IB200}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%

@@

%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}

%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Fossil-calibrated phylogeny and chromosome evolution of Onagraceae}

@@

\address[berk]{Jepson Herbarium and Department of Integrative Biology, University of California, Berkeley}

@@

\paragraph{Supermatrix}

1: Downloads GenBank database of the specified GB division (PLN, MAM, etc)
2: Perform exhaustive all-by-all BLAST comparisons of each ingroup and outgroup sequence.
3: Alternatively (much faster) uses a FASTA file of guide sequences to define each cluster.
   Each ingroup/outgroup sequence is BLASTed against the guide sequences.
   4: Build clusters of sequences:
           - use single-linkage hierarchical clustering algorithm
	           - distance threshold default BLASTn e-value 1.0e-10
		           - uses sequence length percent similarity cutoff default 0.5
			           - discards clusters that are not phylogenetically informative (< 4 taxa)
				   5: Aligns each cluster of sequences using MUSCLE.
				   6: Concatenates the clusters creating a supermatrix.

@@

\begin{figure*}[t]
    \centering
    % have to trim bottom off image
    \includegraphics[width=1.0\textwidth, trim=0 10 0 0, clip=true]{colored_posterior}
    \caption{Phylogeny blah blah blah}
    \label{posteriors}
\end{figure*}

\begin{figure*}[t]
    \centering
    % have to trim bottom off image
    \includegraphics[width=1.0\textwidth, trim=0 10 0 0, clip=true]{time_colored_genera}
    \caption{Phylogeny blah blah blah}
    \label{genera}
\end{figure*}

@@

There are various bibliography styles availablei, please see Figure \ref{genera}. You can select the style of your choice in the preamble of this document. These styles are Elsevier styles based on standard styles like Harvard and Vancouver. Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.
